\usefont{OT1}{bch}{b}{n} \normalfont \normalsize \textsc{School of random department names} \\ [25pt] \horrule{0.5pt} \\[0.4cm] \huge This is the title of the template report \\ \horrule{2pt} \\[0.5cm]

### 2018-06-04 Report/notes.tex
report and maxima

\usepackage[english]{babel}															% English language/hyphenation
\usepackage[protrusion=true,expansion=true]{microtype}	
\usepackage{amsmath,amsfonts,amsthm} % Math packages
\usepackage[pdftex]{graphicx}	
\usepackage{url}

@@

		\begin{figure}
			\centering
			\includegraphics[width=17cm]{picture/distance_hybrid2.png}
			\caption{Euclidean Distance of distribution of the SSP computation between the event model and the PTF model using hybrid engine versus the PTF parameter k,	$t=0.02$,$median lambda$,$\epsilon=10^{-6}$}
			\label{fig:dist_hybrid_50k}
		\end{figure}

>>>>

\usepackage[english]{babel}															% English language/hyphenation
\usepackage[protrusion=true,expansion=true]{microtype}	
\usepackage{amsmath,amsfonts,amsthm} % Math packages
\usepackage[pdftex]{graphicx}	
\usepackage{url}
\usepackage{xcolor}

@@

		\begin{figure}
			\centering
			\includegraphics[width=17cm]{picture/distance_hybrid2.png}
			\caption{Euclidean Distance of distribution of the SSP computation between the event model and the PTF model using hybrid engine versus the PTF parameter k,	$t=0.02$,median $\lambda$,$\epsilon=10^{-6}$}
			\label{fig:dist_hybrid_50k}
		\end{figure}

\clearpage

\section[What has changed ?]{New Model}
\subsection{Changes}

	\begin{figure}[!h]
		\centering
		\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=1.8cm,
		semithick]
		\tikzstyle{every state}=[fill=red,draw=none,text=white]

		\path (s0) edge [bend left]             node {Dirac(t)} (s1)
		(s1) edge [bend left] node {$\lambda$} (s0)
		edge  [bend left]            node {Dirac(t)} (s2)
		(s2) edge [bend left]             node {$\lambda$} (s1)
		edge [bend left]  node {Dirac(t)} (s3)
		(s3) edge [bend left]              node {$\lambda$} (s2)
		edge [bend left]  node {Dirac(t)} (s4)
		(s4) edge [bend left]             node {$\lambda$} (s3)
		edge [bend left]  node {Dirac(t)} (sw)
		(sw) edge [bend left]             node {$\lambda$} (s4)
		edge [bend left]  node {Dirac(t)} (sn)
		(sn) edge [bend left]             node {$\lambda$} (sw);
		\end{tikzpicture}
		\caption{D/M/1/n queue with capacity $n$.Old Event model.}
		\label{fig:Queue_old}
	\end{figure}

	\begin{figure}
		\begin{tikzpicture}[->,>=stealth',shorten >=1pt,auto,node distance=3.0cm,
		semithick]
		\tikzstyle{every state}=[fill=red,draw=none,text=white]

		\node[state] (s0)                    {$n-1$};
		\node[state] (s02) [right of=s0,fill=blue,scale=0.5]                   {};
		\node[state] (s03) [right of=s02,fill=blue,scale=0.5]                    {};
		\node[state] (s04) [right of=s03,fill=blue,scale=0.5]                   {};
		\node[state] (s05) [right of=s04,fill=blue,scale=0.5]                    {};
		\node[state] (s1) [below of=s0]                   {$n$};

		\node[state] (sw0) [above of=s0,fill=white,text=black]        {...}            {};
		\node[state] (sw02) [right of=sw0,fill=white,text=black]        {...}            {};
		\node[state] (sw03) [right of=sw02,fill=white,text=black]        {...}            {};
		\node[state] (sw04) [right of=sw03,fill=white,text=black]        {...}            {};
		\node[state] (sw05) [right of=sw04,fill=white,text=black]        {...}            {};

		\path 
		(s0) 	edge   node {$\lambda$} (sw0)
				edge   node {$\mu$} (s02)
		(sw05)  edge   node {$\lambda$} (s0)		
		(s02)   edge   node {$\lambda$} (sw02)
				edge   node {$\mu$} (s03)
		(s03)   edge  node {$\lambda$} (sw03)
				edge   node {$\mu$} (s04)
		(s04) 	edge  node {$\lambda$} (sw04)
				edge   node {$\mu$} (s05)
		(s05) 	edge  node {$\lambda$} (sw05)
				edge   node {$\mu$} (s1)
		(s1)    edge  node {$\lambda$} (s0);

		\end{tikzpicture}
		\caption{Old Phase Type Model, Production isn't enabled in full queue}
		\label{fig:queue_new}
	\end{figure}

		\path 
		(s0) 	edge [bend left]             node {Dirac(t)} (s1)
		(s1) 	edge [bend left] node {$\lambda$} (s0)
				edge  [bend left]            node {Dirac(t)} (s2)
		(s2)	edge [bend left]             node {$\lambda$} (s1)
				edge [bend left]  node {Dirac(t)} (s3)
		(s3) 	edge [bend left]              node {$\lambda$} (s2)
				edge [bend left]  node {Dirac(t)} (s4)
		(s4) 	edge [bend left]             node {$\lambda$} (s3)
				edge [bend left]  node {Dirac(t)} (sw)
		(sw) 	edge [bend left]             node {$\lambda$} (s4)
				edge [bend left]  node {Dirac(t)} (sn)
		(sn) 	edge [bend left]             node {$\lambda$} (sw)
				edge [loop right]  node {\textcolor{red}{Dirac(t)}} (sn);
		\end{tikzpicture}
		\caption{D/M/1/n queue with capacity $n$. New event Model.}
		\label{fig:event_Queue_new}
	\end{figure}

		\node[state] (s0)                    {$n-1$};
		\node[state] (s02) [right of=s0,fill=blue,scale=0.5]                   {};
		\node[state] (s03) [right of=s02,fill=blue,scale=0.5]                    {};
		\node[state] (s04) [right of=s03,fill=blue,scale=0.5]                   {};
		\node[state] (s05) [right of=s04,fill=blue,scale=0.5]                    {};
		\node[state] (s1) [below of=s0]                   {$n$};

		\node[state] (s12) [right of=s1,fill=blue,scale=0.5]                   {};
		\node[state] (s13) [right of=s12,fill=blue,scale=0.5]                    {};
		\node[state] (s14) [right of=s13,fill=blue,scale=0.5]                   {};
		\node[state] (s15) [right of=s14,fill=blue,scale=0.5]                    {};

		\node[state] (sw0) [above of=s0,fill=white,text=black]        {...}            {};
		\node[state] (sw02) [right of=sw0,fill=white,text=black]        {...}            {};
		\node[state] (sw03) [right of=sw02,fill=white,text=black]        {...}            {};
		\node[state] (sw04) [right of=sw03,fill=white,text=black]        {...}            {};
		\node[state] (sw05) [right of=sw04,fill=white,text=black]        {...}            {};

		\path 
		(s0) 	edge   node {$\lambda$} (sw0)
				edge   node {$\mu$} (s02)
		(sw05)  edge   node {$\lambda$} (s0)		
		(s02)   edge   node {$\lambda$} (sw02)
				edge   node {$\mu$} (s03)
		(s03)   edge  node {$\lambda$} (sw03)
				edge   node {$\mu$} (s04)
		(s04) 	edge  node {$\lambda$} (sw04)
				edge   node {$\mu$} (s05)
		(s05) 	edge  node {$\lambda$} (sw05)
				edge   node {$\mu$} (s1)
		(s1)    edge  node {$\lambda$} (s0)
				edge [red] node {$\mu$} (s12)
		(s12)   edge  node {$\lambda$} (s02)
				edge [red] node {$\mu$} (s13)
		(s13) 	edge  node {$\lambda$} (s03)
				edge [red] node {$\mu$} (s14)
		(s14) 	edge  node {$\lambda$} (s04)
				edge [red] node {$\mu$} (s15)
		(s15) 	edge  node {$\lambda$} (s05)
				edge [red,bend left] node {$\mu$} (s1);
		\end{tikzpicture}
		\caption{New Phase type Model}
		\label{fig:queue_new}
	\end{figure}

\clearpage
\subsection{Result}

\begin{figure}
	\centering
	\includegraphics[width=15cm]{picture/New_model/distance_constant_1E-5.png}
	\caption{Infinite Distance of distribution of the SSP computation between the event model and the PTF model using hybrid engine versus the PTF parameter k,$t=0.1$,median $\lambda$,$\epsilon=10^{-5}$}
	\label{fig:dist_const_1E-5}
\end{figure}

Something is wrong... Maybe $\epsilon$ too big ?

\begin{figure}
	\centering
	\includegraphics[width=17cm]{picture/New_model/distance_epsilon.png}
	\caption{Infinite Distance of distribution of the SSP computation between the event model and the PTF model using hybrid engine versus the PTF parameter k,$t=1$,median $\lambda$,$\epsilon=10^{-5}$}
	\label{fig:dist_epsilon_1E-13}
\end{figure}

\clearpage
\subsection[epsilon termination]{Condition on epsilon termination}
$$\epsilon \leq \frac{\epsilon_{wanted}}{k}$$
$$\forall s \in S, \epsilon \leq Pr(s)$$
$$\epsilon \leq median(Pr(s))$$
$$\epsilon \leq 1stQuartile(Pr(s))$$
$$\epsilon \leq 1stDecile(Pr(s))$$
$$CDF(t-\delta) \leq \epsilon$$
$$\epsilon \leq \frac{1}{|S|}$$
$$\epsilon \leq v = \frac{k}{\lambda^2} = \frac{m^2}{k}$$

\clearpage
\subsection[epsilon termination]{Dynamic Epsilon}

\begin{figure}
	\centering
	\includegraphics[width=17cm]{picture/New_model/distance_explicit_dynamic.png}
	\caption{Absolute Difference between SSP of event model and of SSP PTF model using explicit engine versus state of queue,$t=1$,median $\lambda$,$\epsilon=10^{-5}$}
	\label{fig:dist_dynamic_explicit}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=17cm]{picture/New_model/distance_hybrid_dynamic.png}
	\caption{Absolute Difference between SSP of event model and of SSP PTF model using hybrid engine versus state of queue,$t=1$,median $\lambda$,$\epsilon=10^{-5}$}
	\label{fig:dist_dynamic_hybrid}
\end{figure}
